### 2013-09-08 pystruct/paper.tex
convergence rates, citations, mehr todos fertig...
fixed / improved table of implemented methods

%TODO what about language / license?
\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lcccccc}
\toprule
Package       & Cutting Plane& SSGD & SZLJSP & Latent SSVM & Perceptron & ML\\
\cmidrule(r){1-1} \cmidrule(r){2-7}
\pystruct     & \x        & \x   & \x   & \x          & \x         & \o\\
\svmstruct    & \x        & \o   & \o   & \x          & \o         & \o\\
\sc{Dlib}     & \x        & \x   & \o   & \o          & \x         & \o\\
\sc{CRFsuite} & \o        & \o   & \o   & \o          & \x         & \x\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. SSGD stochastic subgradient decent learning of SSVMs, SZLJSP is
        as described in \secref{dual_coordinate_descent}, Latent SSVM for latent variable SSVMs, ML for
        maximum likelihood learning.}
\end{table}

@@

\section{Summary}
Im this chapter, we introduced basic concepts of structured prediction. In particular, we discussed
Structured Support Vector Machines, a max-margin approach for training linear predictors for
structured data. %TODO comparison of algorithms?
We gave a description of several popular learning algorithms, together with their theoretical
runtime bounds and practical considerations.
%TODO summarize structured prediction
We also introduced \pystruct, our modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations and will be the
basis of our further experiments.
\pystruct integrates itself into the scientific Python ecosystem, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches.
In the future, we plan to integrate other paradigms, such as sampling-based
learning~\citep{wick2011samplerank}, surrogate objectives (for example
pseudo-likelihood), and approaches that allow for a better integration of
inference and learning~\citep{meshi2010learning}.

>>>>

%TODO what about language / license?
\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lccccccc}
\toprule
Package       & 1-SP & $n$-SP & SSGD & SZLJSP & L-SSVM & Perceptron & ML\\
\cmidrule(r){1-1} \cmidrule(r){2-8}
\pystruct     & \x   & \x     & \x   & \x   & \x          & \x         & \o\\
\svmstruct    & \x   & \x     & \o   & \o   & \x          & \o         & \o\\
\sc{Dlib}     & \x   & \o     & \o   & \o   & \o          & \x         & \o\\
\sc{CRFsuite} & \o   & \o     & \o   & \o   & \o          & \x         & \x\\

\bottomrule
\end{tabularx}
    \caption{\label{table:comparision_algorithms}Comparison of learning
        algorithms implemented in popular structured prediction software
        packages. 1-CP stands for 1-slack Cutting Plane, $n$-CP for $n$-slack
        Cutting plane, SSGD for stochastic subgradient decent learning of
        SSVMs, SZLJSP is as described in \secref{dual_coordinate_descent},
        L-SVM stands for latent variable SSVMs, and ML for
        maximum likelihood learning.}
\end{table}

@@

\section{Summary}
Im this chapter, we introduced basic concepts of structured prediction. In particular, we discussed
Structured Support Vector Machines, a max-margin approach for training linear predictors for
structured data. %TODO comparison of algorithms?
We gave a description of several popular learning algorithms, together with their theoretical
runtime bounds and practical considerations.
%TODO summarize structured prediction
We also introduced \pystruct, our modular structured learning and prediction library in Python.
\pystruct is geared towards ease of use, while providing efficient implementations and is be the
basis of our further experiments.
\pystruct integrates itself into the scientific Python ecosystem, making it easy to use with
existing libraries and applications.
Currently, \pystruct focuses on max-margin and perceptron-based approaches.
In the future, we plan to integrate other paradigms, such as sampling-based
learning~\citep{wick2011samplerank}, surrogate objectives (for example
pseudo-likelihood), and approaches that allow for a better integration of
inference and learning~\citep{meshi2010learning}.
